A Framework for Substructural Type Systems \thanks{James Wood is supported by an EPSRC Studentship. Robert Atkey is supported by EPSRC grant FIXME.}

### 2022-01-25 tex/esop22/examples.tex
[ edit ] reify becomes lemma

>>>>

\bob{Reification dumped here for now}
When \AgdaBound{$\V$} supports identity environments (as per \cref{thm:env-id}),
we can simplify our obligations in giving a \AgdaRecord{Semanitics} by coercing
\AgdaFunction{Kripke} functions into just
\AgdaBound{$\C$}-values in an extended context.

%To show this, we instantiate the Kripke function with the renaming
%$\swarrow^r : \Gamma, \gr0\delta \env\sqni \Gamma$ to extend the scope, and
%pass it an argument environment
%$\plr{\id^\V; \searrow^r} : \gr0\gamma, \Delta \env\V \Delta$ to fill in the
%extended part.
%Post-composition of a renaming onto an environment comes from
%\cref{thm:env-postren}.

%\ExecuteMetaData[\Syntactictex]{reify}

\begin{lemma}[\AgdaFunction{reify}]\label{thm:reify}
  If $\V$ is an open family such that there is a function
  $v : \forallb{{\sqni} \dotto \V}$, we get a function of type
  $\forallb{\mathrm{Kripke}\,\V\,\C \dotto \mathrm{Scope}\,\C}$ for any $\C$.
\end{lemma}
\begin{proof}
  Let $b : \mathrm{Kripke}\,\V\,\C\,\Delta\,\Gamma\,A$.
  That is, $b$ is a Kripke function yielding $\C$-computations, and we want to
  apply it so as to get a $\C\,\plr{\Gamma, \Delta}\,A$.
  Let $\grP\gamma = \Gamma$ and $\grQ\delta = \Delta$.
  The $\Box^r$ in the type of $b$ allows us to rename $\Gamma$ to
  $\Gamma, \gr0\delta$.
  Then we give the $\wand$-function an argument in context
  $\gr0\gamma, \Delta$, noting that
  $\plr{\Gamma, \gr0\delta} + \plr{\gr0\gamma, \Delta} = \plr{\Gamma, \Delta}$,
  as we wanted from the result.
  The argument needs type $\gr0\gamma, \Delta \env\V \Delta$.
  We produce this through the composition
  $\gr0\gamma, \Delta \env\V \gr0\gamma, \Delta \env{\sqni} \Delta$,
  using the instance of composition mentioned in \cref{thm:env-postren}.
  The $\V$-environment follows from $v$ and \cref{thm:env-id}, while the
  renaming is the complement to that used on $\Box^r$.
\end{proof}

All of the $\V$s used in examples in this paper support identity environments.
However, \citet[p.~27]{AACMM21} give some important examples that do not
support identity environments, and thus cannot use \AgdaFunction{reify}
(\cref{thm:reify}).
The feature that causes the lack of support for identity environments is that
a semantics can make use of the fact that only variables of particular kinds
are bound by the syntax.
In the examples of \citeauthor{AACMM21}, a bidirectionally typed language only
binds variables that synthesise their type, as opposed to those whose type is
checked.
The semantics of type-checking and elaboration rely on variables synthesising
their type, so \AgdaBound{$\V$} is chosen to cover only those variables.
Instead of using \AgdaFunction{reify}, we must observe that each syntactic form
only binds such synthesising variables.
Similar phenomena would appear in, say, a call-by-value language where
variables are values (not computations), or a polarised language where
variables always have a polarity matching their type.
